Sentinel Likelihood

### 2023-08-23 Data & Scripts/BOUT.Rmd
Aug 23

As random effects, I've chosen the video and individual ID

@@

```{r BOUT MODEL 2}
BOUT.MOD2<-lmer(LDURATION~BEHAVIOR*SENTINEL_PRESENCE+BEHAVIOR*GENERALIZED_ENVIRONMENT+SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+GROUP_SIZE+BAIT_PRESENCE+DISTURBANCE_FREQUENCY+(1|VIDEO_ID/ID), data = BOUT)

>>>>

As random effects, I've chosen the individual ID nested within Video ID.

@@

```{r BOUT MODEL 2}
BOUT.MOD2<-lmer(LDURATION~BEHAVIOR*SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+GROUP_SIZE+BAIT_PRESENCE+DISTURBANCE_FREQUENCY+(1|VIDEO_ID/ID), data = BOUT)

### 2023-08-23 Data & Scripts/PTWY.Rmd
Aug 23

>>>>

## The other variables

We still have bait presence, group size and disturbance frequency to look at. I want to try and make a quick function to run all the tests.

```{r PTWY Vulnerable function}
PTWY.vuln.all<-lapply(PTWY[,c("SENTINEL_PRESENCE"
                              ,"GENERALIZED_ENVIRONMENT"
                              , "GROUP_SIZE"
                              , "BAIT_PRESENCE"
                              , "DISTURBANCE_FREQUENCY")
                              ]
                         , function(x) MANOVA.wide(cbind(PTWY$PTWY_HD.HDP, PTWY$PTWY_HU.HD)~x, data = PTWY, iter = 1000)
                         )
PTWY.SENT<-summary(PTWY.vuln.all$SENTINEL_PRESENCE)
PTWY.GENV<-summary(PTWY.vuln.all$GENERALIZED_ENVIRONMENT)
PTWY.GS<-summary(PTWY.vuln.all$GROUP_SIZE)
PTWY.BP<-summary(PTWY.vuln.all$BAIT_PRESENCE)
PTWY.DF<-summary(PTWY.vuln.all$DISTURBANCE_FREQUENCY)
```

### 2023-08-23 Data & Scripts/SENT.Rmd
Aug 23

We will be reusing the 'Single Row' dataset for this script.

@@

```{r SENT Subset}
SENT<-SENT[1:81,c(1,2,7,10,11,15,17,20,22,30,31)]
str(SENT)
dim(SENT)
```
81 observations across 9 variables. BUT that's with all the individuals. Let's remove those replicates.

@@

```{r Chi Square}
library(descr)
library(MASS)
CHISQ<-lapply(SENT[,c("GENERALIZED_ENVIRONMENT"
                                 , "GROUP_SIZE"
                                 , "DISTURBANCE_FREQUENCY")
                              ]
                         , function(x) CrossTable(x,SENT$SENTINEL_PRESENCE
                                                  , fisher = T
                                                  , chisq = T
                                                  , expected = T
                                                  , prop.c = F
                                                  , prop.t = F
                                                  , prop.chisq = F
                                                  , sresid = T
                                                  , format = 'SPSS')
                         )

>>>>

We will be reusing the 'Single Row' data set for this script.

@@

```{r SENT Subset}
SENT<-SENT[1:81,c(1,2,7,10,11,15,17,19,20,22,30,31)]
str(SENT)
dim(SENT)
```
81 observations across 9 variables. BUT that's with all the individuals. Let's remove those replicates.

@@

```{r Chi Square}
library(descr)
library(MASS)
CHISQ<-lapply(SENT[,c("GENERALIZED_ENVIRONMENT"
                      , "GROUP_SIZE"
                      , "DISTURBANCE_FREQUENCY"
                      , "BAIT_PRESENCE")
                              ]
                         , function(x) CrossTable(x,SENT$SENTINEL_PRESENCE
                                                  , fisher = T
                                                  , chisq = T
                                                  , expected = T
                                                  , prop.c = F
                                                  , prop.t = F
                                                  , prop.chisq = F
                                                  , sresid = T
                                                  , format = 'SPSS')
                         )
